---
title: "R markdown"
date: "2018-03-21"
output:
  xaringan::moon_reader:
    css: [default, metropolis, metropolis-fonts]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

class: inverse, center, middle

# R markdown

*Author PDF, Word files, slides and more*

---

# Why use it?

--

### communicating 

--

### collaborating

--

### environment

---

# What is it? 

## rmarkdown -> knitr -> markdown -> pandoc -> ...

## A minimal example (minimal.Rmd)

---

# Examples

 - These slides!

 - Smaller processing tasks (short-example.Rmd)
 
 - Larger more involved reports (e.g. tech reports / thesis / publications) containing charts, tables, references
 
 - Interactive reports https://github.com/LCisannoyed/ShinyExample
 
 - Websites https://markdly.github.io/arc/
 
 - ...

---

# Shiny 

https://edmeasurement.shinyapps.io/dashboard/

---

# Content examples

Adapted or taken from [**xaringan**](https://github.com/yihui/xaringan) default template

---

# Math Expressions

You can use LaTeX for things like math expressions.  For example, this code:

```
$$\bar{X}=\frac{1}{n}\sum_{i=1}^nX_i$$
```

Once rendered will display like this

$$\bar{X}=\frac{1}{n}\sum_{i=1}^nX_i$$

---

# R Code

```{r comment='#'}
set.seed(123)
sample(LETTERS, 5)

```

---

# R Plots

```{r cars, fig.height=4, dev='svg'}
plot(cars)
```

---

# Tables you can navigate

```{r eval=require('DT'), tidy=FALSE}
DT::datatable(
  head(iris, 10),
  fillContainer = FALSE, options = list(pageLength = 5)
)
```

---

# References

Slides created via the R package [**xaringan**](https://github.com/yihui/xaringan).

Under the hood [remark.js](https://remarkjs.com), [**knitr**](http://yihui.name/knitr), and [R Markdown](https://rmarkdown.rstudio.com).
